Kids LRTI tracking

### 2020-04-09 exposure_initial_analysis.Rmd
exposure and lrti analysis updates

---
title: "KidsAIR: initial exposure analysis"
author: "Ethan Walker"
date: "Started 2 Feb 2020, Updated 3 April 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
```

@@

>>>>

---
title: "KidsAIR: initial exposure analysis"
author: "Ethan Walker"
date: "Started 2 Feb 2020, Updated 9 April 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
library(mctest)
library(ppcor)
library(GGally)
library(tidyverse)
```

@@

# Run correlations/Chi-square tests between different covariates
Goal is to check for vars that have a lot of overlap and eliminate some from
consideration to include in models
```{r}
pm_mean_sampling_period <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  dplyr::select(pm_mean_sampling_period, education_3level, income_3level,
                race_parent, race_child, total_residents_2level, 
                residents_under5_2level, residents_smoke,
                stove_grade_3level, burn_level_3level, wood_cords,
                mean_moisture_winter) %>% 
  mutate_all(as.numeric) %>% 
  na.exclude() %>% 
  dplyr::select(pm_mean_sampling_period)

other_vars <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  dplyr::select(pm_mean_sampling_period, education_3level, income_3level,
                race_parent, race_child, total_residents_2level, 
                residents_under5_2level, residents_smoke,
                stove_grade_3level, burn_level_3level, wood_cords,
                mean_moisture_winter) %>% 
  mutate_all(as.numeric) %>% 
  na.exclude() %>% 
  dplyr::select(-pm_mean_sampling_period)

omcdiag(other_vars, pm_mean_sampling_period)

imcdiag(other_vars, pm_mean_sampling_period)
imcdiag(other_vars, pm_mean_sampling_period, method = "Wi")
```

# Try individual chi-square tests and correlations b/w two vars
```{r}
chisqu_results <- chisq.test(chisqu_data_demographics$education_3level, 
                             chisqu_data_demographics$income_3level)
chisqu_results

chisqu_results <- cor.test(chisqu_data_demographics$education_3level, 
                             chisqu_data_demographics$income_3level)
chisqu_results

ggpairs(chisqu_data_demographics)
```

### 2020-04-09 lrti_tracking.Rmd
exposure and lrti analysis updates

---
title: "Kids LRTI tracking"
author: "Ethan Walker"
date: "Started 6 April 2020, Updated 8 April 2020"
output: pdf_document 
---

@@

Other questions:
- How far has the team made it (date/winter) in diagnosing LRTI? Winter 17/18?
- Has this process been done/started for NN/AK, or just WMT?

```{r}
# LRTI Diagnosis data
lrti_diagnosis_data <- health_exposure_data_sampling_day %>% 
  # select relevant health data
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         med_visit_date:med_visit_mean_temp,
         csq_date:csq_comments, 
         med_rec_visit_date, med_rec_dr_diagnosis, med_rec_ari, med_rec_comments,
         lrti_number:lrti_professional_comments) %>% 
  # Currently only have this data for WMT - need to get new files and updates dataset
  filter(area == "WMT") %>% 
  # This is the most broad way of distinguishing if a child was sick
  # Need to get Paul's protocol for diagnosis to filter down from here
  filter(csq_sick_2_weeks == "Yes") 
```

>>>>

---
title: "Kids LRTI tracking"
author: "Ethan Walker"
date: "Started 6 April 2020, Updated 9 April 2020"
output: pdf_document 
---

@@

Other questions:
- LRTI and ARI have been used interchangably. Our actual outcome is LRTI, yes?
  - Is there a clinical definition we/Paul have been following when diagnosing cases?
  - LRTI: bronchiolitis, pneumonia, croupe? Case definition up to Paul.
  - Primary diagnosis is based on med recs, but secondary outcomes could be from
    surveys. Also see how well survey data predicts Pauls diagnosis.
- How does Paul initially narrow down which cases to look at? Or does he look
  at each CSQ and med visit form?
- How far has the team made it (date/winter) in diagnosing LRTI? Winter 17/18?
  - Could touch base with Nick, but probably through winter 17/18.
- Has this process been done/started for NN/AK, or just WMT?
  - No. Surveys may be worse for these areas, but med rec data could be better
    through Indian Health Services.
  - At risk period could be difficult for these sites
- Where did the med_visit_ari variable come from?

Notes and specific documentation for steps to identify LRTI cases:
- Double check the filter method of "yes" for sick/still sick
- Ask Kathrene about med rec ARI vs med visit ARI and where they came from
- Was there a variable where parents called us to report sickness?
-

Next steps
- Ask Kathrene some questions from above
  - Have her upload final health data for NN/AK
- Push to get the final data input, QA/QC, uploaded to Box
- Go through winter 18/19 data line by line and flag cases that could be 
  respiratory.
  - Do this for all sites, and start on other sites for all years.
- Also flag other potential secondary outcomes that we could look at.

```{r}
# LRTI Diagnosis data
lrti_diagnosis_data <- health_exposure_data_sampling_day %>% 
  # select relevant health data
  select(area, home, home_winter_id, winter_id, child_id_num, 
         visit_date, med_visit_date, med_visit_referred,
         csq_date:csq_symptom_free_date,
         csq_see_dr, csq_dr_diagnosis,
         med_rec_visit_date:med_rec_comments,
         csq_miss_work:csq_comments,
         med_visit_ari:med_visit_mean_temp,
         lrti_number:lrti_professional_comments) %>% 
  # Currently only have this data for WMT - need to get new files and updates dataset
  filter(area == "WMT") %>% 
  # This is the most broad way of distinguishing if a child was sick
  # Careful when filtering here. Could still make cases that these vars didn't catch
  # Best to have a look through all rows, then use this to filter data down so it
  # is easier to work with to assess dates/at-risk times
  filter(csq_sick_2_weeks == "Yes" | csq_still_sick == "Yes") %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  ungroup()

#  filter(visit_date > "2018-06-01") # filter for newer data by date

# write_rds(lrti_diagnosis_data, "Output/lrti_diagnosis_data.rds")
# write_csv(lrti_diagnosis_data, "Output/lrti_diagnosis_data.csv", na = " ")
```
